---
title: "MS2 Yuda"
output: html_document
date: "2023-11-19"
---

## Description
The Fortune 1000 dataset is from the Fortune website, containing U.S. company data for the year 2022. I implement an interactive with Shiny App. Users can select the ranges of rank and employee numbers via two slider inputs to get a subset of the 1000 companies, then it will demonstrate the total revenue across sectors via a pie chart and a box plot, the number of companies across sectors via another pie chart, and the total revenue across states via a heat map on a U.S. map.

```{r}
rm(list = ls())
library(tidyverse)
library(ggplot2)
library(shiny)
library(maps)
library(dplyr)
library(tmap)
library(tmaptools)
library(sf)
library(tigris)
library(plotly)
data <- read_csv('Fortune_1000.csv')
data <- data[,1:9]
names(data)[6] <- 'employees'
data <- data[!is.na(data$employees),]
```
```{r}
#Create the UI
ui <- fluidPage(
  fluidRow(
    column(6,sliderInput('rank', 'Fortune Rank', max = max(data$rank), min = min(data$rank),c(1,1000), sep = '')),
    column(6,sliderInput('employees', 'Company employees', max = max(data$employees), min = min(data$employees),c(160,2300000)))
  ),
  fluidRow(
    column(6, plotOutput("piecount")),
    column(6, plotOutput("piereven"))
  ),
  fluidRow(
    column(12, plotOutput("boxreven"))
  ),
  fluidRow(
    column(12, plotOutput("mapreven"))
  )
)

#Create the plot functions
piecount <- function(data){
  data_summary <- data |>
    group_by(sector) |>
    summarise(count = n())
  ggplot(data_summary, aes(x = '', y = count, fill = sector)) +
    geom_bar(width = 1, stat = "identity") +
    coord_polar(theta = "y") +
    labs(fill = "sector",
         title = "Company number - Sectors") +
    theme_void()
}

piereven <- function(data){
  data_summary <- data |>
    group_by(sector) |>
    summarise(sum = sum(revenue))
  ggplot(data_summary, aes(x = '', y = sum, fill = sector)) +
    geom_bar(width = 1, stat = "identity") +
    coord_polar(theta = "y") +
    labs(fill = "sector",
         title = 'Total Revenue - Sectors') +
    theme_void()
}

boxreven <- function(data){
  data |>
    filter(revenue >= quantile(data$revenue, 0.25), revenue <= quantile(data$revenue, 0.75)) |>
  ggplot()+
    geom_boxplot(aes(x = sector, y = revenue, fill = sector),outlier.shape = NA)+
    xlab('')+
    labs(title = 'Total Revenue - Sectors')+
    theme(axis.text.x = element_blank())
}

mapreven <- function(data){
  us_geo <- tigris::states(class = "sf")[,c('REGION','STUSPS','geometry')]

  data_summary <- data |>
    group_by(state) |>
    summarise(sum = sum(revenue))

  map_data <- left_join(us_geo, data_summary, by = c("STUSPS"="state")) |>
    filter(REGION != 9) |>
    shift_geometry()

  map_data$sum[is.na(map_data$sum)] <- 0 

  tm_shape(map_data) +
    tm_borders() +
    tm_fill(col = "sum", palette = "Blues", title = 'Total Revenue - States') +
    tm_layout(legend.outside = TRUE)
}

server <- function(input, output){
    data_subset <- reactive({
    data |>
      mutate(selected = (
        (rank >= input$rank[1]) &
        (rank <= input$rank[2]) &
        (employees >= input$employees[1]) &
        (employees <= input$employees[2])
      )) |>
      filter(selected)
  })
    
    output$piecount <- renderPlot({
      piecount(data_subset())
    })
    output$piereven <- renderPlot({
      piereven(data_subset())
    })
    output$boxreven <- renderPlot({
      boxreven(data_subset())
    })
    output$mapreven <- renderPlot({
      mapreven(data_subset())
    })
}

#shinyApp(ui, server)
```












